Probability Distribution Checks

### 2017-04-25 Probability_distribution_checks.Rmd
Revise analysis and data handling
**_THIS IS BEING REVISED_**

The original analysis is unlikely to be the correct approach. The data
are being examined again and a new analysis will be conducted that
accounts for the ordinal scale used for data collection for severity.

The data are now in a tidy data frame and are ready for checking

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked, for my purposes normal or exponential are enough so I won't check the others.

## 2015 Check probability distribution fit for leaf sheath blight

@@

f1 <- fitdist(AUDPS_2015$LShB_AUDPS, "norm")
plot(f1)
qqp(AUDPS_2015$LShB_AUDPS, "norm")

f2 <- fitdist(AUDPS_2015$LShB_AUDPS, "exp")
plot(f2)
qqp(AUDPS_2015$LShB_AUDPS, "exp")

## 2015 Check probability distribution fit for tiller sheath blight

f1 <- fitdist(AUDPS_2015$TShB_AUDPS, "norm")
plot(f1)
qqp(AUDPS_2015$TShB_AUDPS, "norm")

f2 <- fitdist(AUDPS_2015$TShB_AUDPS, "exp")
plot(f2)
qqp(AUDPS_2015$TShB_AUDPS, "exp")

@@

## 2016 Check probability distribution fit for leaf sheath blight

@@

f1 <- fitdist(AUDPS_2016$LShB_AUDPS, "norm")
plot(f1)
qqp(AUDPS_2016$LShB_AUDPS, "norm")

f2 <- fitdist(AUDPS_2016$LShB_AUDPS, "exp")
plot(f2)
qqp(AUDPS_2015$LShB_AUDPS, "exp")

## 2016 Check probability distribution fit for tiller sheath blight

f1 <- fitdist(AUDPS_2016$TShB_AUDPS, "norm")
plot(f1)
qqp(AUDPS_2016$TShB_AUDPS, "norm")

f2 <- fitdist(AUDPS_2016$TShB_AUDPS, "exp")
plot(f2)
qqp(AUDPS_2015$LShB_AUDPS, "exp")

>>>>

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked.

## 2015 Check probability distribution fit for tiller sheath blight incidence

@@

f1 <- fitdist(DS2015$TShB_incidence, "norm")
plot(f1)
car::qqp(DS2015$TShB_incidence, "norm")

f2 <- fitdist(DS2015$TShB_incidence, "exp")
plot(f2)
car::qqp(DS2015$TShB_incidence, "exp")

@@

## 2016 Check probability distribution fit for tiller sheath blight incidence

@@

f1 <- fitdist(DS2016$TShB_incidence, "norm")
plot(f1)
car::qqp(DS2016$TShB_incidence, "norm")

f2 <- fitdist(DS2016$TShB_incidence, "exp")
plot(f2)
car::qqp(DS2016$TShB_incidence, "exp")
